Provisional Title

### 2021-04-30 draft/draft.tex
more fig1 and draft

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=12cm,keepaspectratio]{figs/fig1.pdf}
\caption{\textbf{Overview of the experimental protocol.}
\textbf{a.}~Environmental samples obtained from eight different locations were used
to inoculate our communities.
\textbf{b.}~Communities were stabilized in serial batch culture bioreactors
\cite{Goldford2018} in minimal synthetic media with glutamine or citrate as the
only supplied carbon source.
\textbf{c.}~Communities were plated in minimal media agar plates and the most abundant
species (the ``dominants") from each community were isolated. We refer to the set of
sub-dominant species as the ``cohorts".
\textbf{d.}~Rank-frequency distributions of all eight communities stabilized in either
glutamine (red) or citrate (blue), sequenced at a depth of $10^{-4}$ reads.
Three biological replicates per community are shown.
Community compositions are skewed and long-tailed.
\textbf{e.}~Our hypothesis is that ecological co-selection can take place from the top-down,
i.e. the dominant co-selecting the cohort, or from the bottom-up, i.e. the cohort co-selecting
the dominant. Both forms of co-selection can be positive (recruitment) or negative
(antagonism).
\textbf{f.}~Illustration of the protocol of our coalescence experiments.}
\label{fig1}
\end{figure}
